---
title: "Statistical Learning"
author: "Masoud Faridi"
date: "2024-09-28"
output: pdf_document
  beamer_presentation: default
  pdf_document:
    latex_engine: xelatex
    
header-includes:
- \usepackage[document]{ragged2e}
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
- \usepackage{float}
- \usepackage{array}
- \usepackage{fancyhdr}
- \usepackage{graphicx}
- \usepackage{hyperref}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What Is Statistical Learning?

\justify

Suppose that we observe a quantitative response $Y$ and $p$
different predictors, $X_1, X_2, \cdots , X_p$. We assume that there is some
relationship between $Y$ and $X = (X_1, X_2, \cdots , X_p)$, which can be written
in the very general form $Y = f(X) + \epsilon$.

Here $f$ is some fixed but unknown function of $X_1, . . . , X_p$, and $\epsilon$ is a random
error term, which is independent of $X$ and has mean zero. In this formulation, $f$ represents the systematic information that $X$ provides about $Y$.

Consider a given estimate $\hat{f}$ and a set of predictors $X$, which yields the
prediction $\hat{Y} = \hat{f}(X)$. Assume for a moment that both $\hat{f}$ and $X$ are fixed,
so that the only variability comes from $\epsilon$. Then, it is easy to show that

$$\begin{aligned}
E(Y-\hat{Y} )^2 = E\left(f(X) + \epsilon - \hat{f}(X) \right)^2 &=\left(f(X) - \hat{f}(X) \right)^2+\text{Var}(\epsilon) \\
&= \underbrace{[f(X) - \hat{f}(X)]^2}_{\text{Reducible}} + \underbrace{\text{Var}(\epsilon)}_{\text{Irreducible}} 
\end{aligned}
$$



where $E(Y - \hat{Y} )^2$ represents the average, or expected value, of the squared expected
value difference between the predicted and actual value of $Y$ , and $\text{Var}(\epsilon)$ 
  represents the variance associated with the error term $\epsilon$.
The focus  is on techniques for estimating $f$ with the aim of
minimizing the reducible error. It is important to keep in mind that the
irreducible error will always provide an upper bound on the accuracy of
our prediction for $Y$ . This bound is almost always unknown in practice.


This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

